Storm Surges

### 2014-01-31 RoughWork/manuscript.tex
Added information about the open boundaries, values and conditions.

\subsubsection{Temperature and salinity}
Temperature and salinity at the Juan de Fuca boundary were taken from a climatology which was created from observations collected by (which Masson ref?) over the period of 19??-2004?.

\subsection{Initial conditions}

@@

>>>>

\subsubsection{Temperature and salinity}
Temperature and salinity at the Juan de Fuca boundary were taken from a weekly climatology which was created from results from a model covering the Salish Sea and the west coast of Vancouver Island \citep{massonfine2012}.  Their results, originally on s-levels were interpolated onto z-levels and then onto the NEMO horizontal grid.  To prepare the climatology all years (1995-2008) were averaged and results, approximately every 15 days, were interpolated to a weekly climatology.

\subsubsection{Sea Surface Height}
Sea surface height at the mouth of Juan de Fuca was set using values from the Tofino tide guage.  A monthly climatology was produced using daily averages from 2000-2010, binning them by month, averaging and setting the yearly mean to zero.  For the storm surge simulations, hourly variations in sea surface height were used.  These values are the Tofino tide guage values, de-tided and with the zero reset as for the climatology.

\subsubsection{Open Boundary Conditions}

The model relaxed to the forced temperature and salinity over the 10 grid points (about 5km) closest to the open boundaries, using the NEMO FRS scheme \cite.  The tidal forcing and sea surface height was used in the barotropic velocity forcing which used the NEMO Flather scheme \cite  The baroclinic velocities at the boundary were set to be equal to the values inside the boundary (zero-gradient boundary conditions).  This scheme is not part of core NEMO.  Zero gradient conditions were chose because the baroclinic velocity at the mouth of Juan de Fuca is primarily estuarine and thus set by density variations between inside and outside the domain.

@@

\subsection{Initial conditions}
Initial conditions for temperature and salinity were taken from a CTD cast in the middle Strait of Georgia taken in Sept 2002 \citep{pawlowiczetal2007}.  Conditions were initially uniform horizontally.  Velocity was initialized at zero.

\subsection{Spin-up}
The model was spun up for a 15.5 months from the initial conditions above, starting Sep 16, 2002, using atmospheric forcing from 2002-2003, climatological temperature and salinity and sea surface height at the boundaries, with tides and climatological river output.  All storm surge runs were started.....
